---
title: "MnA Coeff Cutoff"
author: "Dan Zylberglejd and Noam Habot"
date: "5/8/2017"
output: pdf_document
---
```{r}
############################################################################################################
# This is an analysis file to determine the cutoff points between top/bottom law firms
#     where the top/bottom is chosen according in a couple of different methods.
#
# Ways that top/bottom law firms are decided:
#   1) (Gross Revenue) / (Number of Lawyers)
#           - with a rolling cutoff from the top tier being the top 5 to the top tier being the top 120
#                 as ranked by the outcome=(Gross Revenue)/(Number of Lawyers)
#   2) Individual MnA
#           - the cutoff being Mna>0 and MnA=0
#
# We use a logistic regression model to predict whether a given data point will be classified
#       as top or bottom. The model is trained on the entire data set.
#
#
# DEFINITION of "cutoff" value:
#   A "cutoff" value is defined as the number of firms that are in the "top tier", and (n-cutoff) is the number in the bottom tier
#
#
# Decisions:
#   1) the rolling window in number of years - determines how many years to look back from 2015
#           - i.e. if rollingWindow = 5, then data will be considered from all of 2011 to all of 2015
#   2) which variables and plots to create at the end to show the results
#
# Created by Dan Zylberglejd and Noam Habot
############################################################################################################
```


```{r}
##### Clear environment
rm(list = ls())

##### Load libraries
#detach("package:MASS", unload=TRUE)
library(dplyr)
library(plm)
library(lmtest)
library(sandwich)
library(multiwayvcov)
library(ggplot2)
library(data.table)
require(strucchange)


##### Load dataframe
setwd("~/Google Drive/Stanford Law Project")
load('Data/EliteLawDf.RData')
```

We here write a function that will take in a the accuracy data frame from a specific run and find the cutoff range.  
We define a "cutoff range" as the range of 5 points that we can consider to be the cutoff.  
We will assign the "cutoff" to be the middle number in this range.
```{r}
# perform a sliding range analysis from cutoff=5 onwards, and see where is the first 5-point range that we see a significant difference
# continue this sliding range for a length of about 10 more points and see that we do have a max; otherwise, assign the cutoff to the new range


findCutoffRange <- function(accuracy, maxInThisDataSet, beginningOfCutoff) {
  range <- beginningOfCutoff:(beginningOfCutoff+4)
  cutoffRange <- range
  largestDiff <- 0
  i <- 9
  while (i <= maxInThisDataSet-5) {
    thisDiff <- max(accuracy[range])-min(accuracy[range])
    #print(paste("i=", i, "thisDiff=", thisDiff, "range=", range))
    if (thisDiff > largestDiff) {
      largestDiff <- thisDiff
      cutoffRange <- range
    }
    range <- range + 1
    i <- i + 1
  }
  return(cutoffRange)
}


# this is a function that can only be run after "wholeResults" has been created.
# it plots the accuracies and cutoffs for the data in that row
plotRowI <- function(rowToVisualize) {
  ggd <- data.frame(accuracy=wholeResults$Accuracies[rowToVisualize][[1]], x=1:length(wholeResults$Accuracies[rowToVisualize][[1]]))
  oc <- wholeResults$OptimalCutoff[rowToVisualize]
  
  title <- "Accuracy vs. Cutoff"
  if (wholeResults$Firm[rowToVisualize] == "All")  {
    title <- paste(title, "- All Firms")
  }
  if (wholeResults$YearFrom[rowToVisualize] == wholeResults$YearTo[rowToVisualize]) {
    title <- paste(title, "in", wholeResults$YearTo[rowToVisualize])
  } else {
    title <- paste(title, "from", wholeResults$YearFrom[rowToVisualize], "to", wholeResults$YearTo[rowToVisualize])
  }
  
  p <- ggplot(data=ggd, aes(x=x, y=accuracy)) +
      geom_line(color="red") +
      geom_point() + ggtitle(title) + xlab("Cutoff") + ylab("Accuracy (%)") +
      geom_vline(xintercept=oc, linetype="dotted") + 
      geom_text(aes(x=oc, label=paste("Cutoff =",oc), y=quantile(ggd$accuracy, na.rm=TRUE, 0.1)), colour="black", angle=90, text=element_text(size=11)) +
      labs(caption = "Note: the Cutoff value represents the number of firms that are in the Top Tier")# +
      #geom_text(data=subset(results, name>=(oc-2) & name <= (oc+2)), aes(x=(oc-2):(oc+2), accuracy,label=name))
  
  # plot the individual MnA as a proportion of its highest MnA
  #if (wholeResults[rowToVisualize, "Firm"] != "All") {
  #  p + ggplo
  #}
  show(p)
}


maximums <- function(x) which(x - shift(x, 1) > 0  & x - shift(x, 1, type='lead') > 0)
minimums <- function(x) which(x - shift(x, 1) < 0  & x - shift(x, 1, type='lead') < 0)
```

Here we use a dependent variable $Outcome=\frac{GrossRevenue}{Lawyers}$ as the outcome variable in the model, with the cutoff ranging from the top 5 to the top 120 firms (as ranked by the outcome variable).
```{r}
beginningOfCutoff <- 9
shouldSave <- FALSE

# deletes an existing and creates a new wholeResults table
wholeResults <- data.frame(Firm=character(0), YearFrom=numeric(0), YearTo=numeric(0),
                           NumYears=numeric(0), OptimalCutoff=numeric(0), NumInSample=numeric(0), OptimalCutoffDividedByNumInSample=numeric(0),
                           fValue=numeric(0), pValue=numeric(0), stringsAsFactors=FALSE)

# Various data queries
#wholeResults[nrow(wholeResults) + 1, c("Firm", "YearFrom", "YearTo")] <- list("Baker & Hostetler", 1984, 2015)


wholeResults[nrow(wholeResults) + 1, c("Firm", "YearFrom", "YearTo")] <- list("All", 2013, 2013)
wholeResults[nrow(wholeResults) + 1, c("Firm", "YearFrom", "YearTo")] <- list("All", 2014, 2014)
wholeResults[nrow(wholeResults) + 1, c("Firm", "YearFrom", "YearTo")] <- list("All", 2015, 2015)



# gets the cutoff values for all the firms for each year
#for (y in unique(df$Year)) {
#  wholeResults[nrow(wholeResults) + 1, c("Firm", "YearFrom", "YearTo")] <- list("All", y, y)
#}



# Set the output
Output = df$GrossRev/df$Lawyers
# Set the main covariates
covariates = df %>% select(FirmName, Year, Lawyers, Lawyers2, MnA, Equity, IPO, Leverage)

# Get factor variables Year and Firm
#years = data.frame(Years = as.factor(df$Year - min(df$Year) + 1))
#firms = data.frame(FirmID = as.character(df$FirmID))

# Merge into one main dataset
dataset = cbind(Output, covariates)
dataset = dataset %>% na.omit()

for (i in 1:nrow(wholeResults)) {
  print(paste("Working on row:", i, "out of", nrow(wholeResults)))
  
  ##### Initialization variables
  # YearFrom, YearTo
  yearFrom <- wholeResults[i, "YearFrom"]
  yearTo <- wholeResults[i, "YearTo"]
  wholeResults[i, "NumYears"] <- yearTo-yearFrom+1
  
  
  # Dataframes for results
  #results = data.frame(numConsidered=numeric(0), fValue=numeric(0), pValue=numeric(0))
  
  
  # Get the current dataset ready
  currDataset = dataset %>% filter(Year >= yearFrom) %>% filter(Year <= yearTo)
  if (wholeResults[i, "Firm"] != "All") {
    currDataset = currDataset %>% filter(FirmName == wholeResults[i, "Firm"])
  }
  # Sort data frame by decreasing Output variable
  currDataset <- currDataset[order(currDataset$Output, decreasing=TRUE),]
  
  wholeResults[i, "NumInSample"] <- nrow(currDataset)
  
  
  
  #for(cutoff in beginningOfCutoff:(nrow(currDataset)-beginningOfCutoff)){

    # run the Chow test on it at point=cutoff
  #  test <- sctest(Output ~ Year + Lawyers + Lawyers2 + MnA + Equity + IPO + Leverage, type = "Chow", point = cutoff, data = currDataset[,-2])
  #  m <- breakpoints(Output ~ Year + Lawyers + Lawyers2 + MnA + Equity + IPO + Leverage, data=currDataset[,-2])
    
    # Populate results table
  #  results[cutoff, "numConsidered"] = nrow(currDataset)
  #  results[cutoff, "fValue"] = test$statistic
  #  results[cutoff, "pValue"] = test$p.value
  #}
  #b <- breakpoints(Output ~ Lawyers + Lawyers2 + MnA + Equity + IPO + Leverage, data=currDataset, h=8)
  b <- breakpoints(Output ~ MnA, data=currDataset, h=8, breaks=1)
  print(b$breakpoints)
  #b <- breakpoints(Output ~ 1, data=currDataset, breaks=1, h=8)
  
  #optimalCutoff <- which.max(results$fValue)
  optimalCutoff <- b$breakpoints[1]
  wholeResults[i, "OptimalCutoff"] <- optimalCutoff
  wholeResults[i, "OptimalCutoffDividedByNumInSample"] <- optimalCutoff/nrow(currDataset)
  #wholeResults[i, "fValue"] <- results$fValue[optimalCutoff]
  #wholeResults[i, "pValue"] <- results$pValue[optimalCutoff]

}
```

```{r}
ggplot(data=results, aes(x=1:nrow(results), y=fValue)) + geom_line(aes(color="red"), size=1.5) + geom_point(size=0.5) +
  ggtitle(paste("Chow Test - Fvalues over Cutoffs for all firms in", "2007")) + theme(legend.position="none") +
  xlab("Cutoff") + ylab("F Value") + labs(caption = paste("Cutoff that maximizes F-value:", which.max(results$fValue)))
```

To save the wholeResults table:
```{r, eval=FALSE}
#if (shouldSave) {
#  save(wholeResults, file = 'Data/YearlyCutoffAccuracies.RData')
#}
```

Here we use the independent variable *Individual MnA* as the output, with the cutoff being firms with $MnA>0$ and those with $MnA=0$.
```{r}
##### Initialization variables
# Rolling window, in number of years

results = data.frame(accuracy=numeric(0), numPredicted=numeric(0), MnACoeff=numeric(0))

for (rollingWindow in 1:20) {
  # Set the main covariates
  dataset = df %>% select(MnA, FirmName, Year, Lawyers, Lawyers2, Equity, IPO, Leverage, GrossRev)
  
  # Merge into one main dataset
  dataset = dataset %>% na.omit() %>% filter(Year <= 2015) %>% filter(Year >= 2015 - rollingWindow + 1)
  
  
  # Create the 2 groups
  #currDataset = currDataset %>% mutate(isTop = Output>=outputCutoff) 
  dataset = dataset %>% mutate(isTop = MnA>0)
  
  # Run model
  model = glm(isTop ~ ., data = dataset[,-2]) # remove the firm name from model
  
  # Extract results
  coeffs = summary(model)$coefficients[, 1]
  predictions = predict(model, newdata=dataset[,-2], type="response") # remove the firm name from model
  predictions = predictions > 0.5
  accuracy = sum(predictions==dataset$isTop) / nrow(dataset)
  numPredicted = sum(predictions)
  
  

  # Populate results table
  results <-rbind(results, data.frame("accuracy"=accuracy, "numPredicted"=sum(predictions), "MnACoeff"=coeffs["MnA"]))
}

rownames(results) <- 1:nrow(results)
ggplot(data=results, aes(x=1:nrow(results), y=accuracy)) + geom_line() +  geom_point(color="red") +
  ggtitle("Accuracy of Top = (Mna > 0) relative to Rolling Window") + ylab("Accuracy (%)") + xlab("Rolling Window (Years)")


results
```